### 2021-03-11 results/draft.tex
small changes
changed fig1
revised the first paragraph in Introduction

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a essential issue in ecology.
Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity (面倒なのでレビュー論文を引用) because the surveys of eDNA are easy to detect presence/absence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015 %Dorazioに引用されていたやつ．あとで再確認).
%Field survey using eDNA is easy to detect presence/absence of target species, non-invesiveness, and high cost effectiveness rather than previous direct sampling methods such as visual or aural, so that eDNA is widely used to detect invesive species, rare species, and hot spot of biodiversity.
However, the presence/absence of eDNA includes many types of uncertainties due to relating to environmental factors such as temperature and advection ().
For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.
Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.

@@

\flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
To estimate the spatial distribution of four focal species using eDNA and catch data by considering with spatial  uncertainties of eDNA, we fitted the model (equation 1) to the presence/absence of eDNA and of catch collected in Tokyo Bay as follows:
%In this study, to estimate the spatial distribution of species from eDNA considering with spatial uncertainties, we make a integrated species distribution model using correlation method.
\[
\mathrm{logit} \ \ p_{e}(s_{i}) = \alpha_{e} + \sum_{k}f_{k}(x_{k}(s_{i})) + w \theta(s_{i}) + u_{e}(s_{i})
\]
\[
\mathrm{logit} \ \ p_{c}(s_{i}) = \alpha_{c} + \beta_{i} + \theta(s_{i}) + u_{c}(s_{i})
\]
where $\alpha$ is the intercept, and $x_{k}(s_{i})$ is the covariates at sites $i$ for occurrence probabilities of eDNA at sites $i$. In the study, seawater temperature, salinity, pH, and DO were used as covariates which effect on the occurrence of eDNA (i.e., $k = 4$). $u(s_{i})$ is spatial error that is specific for each data following multivariate normal distributions $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function. $\theta$ which is shared between eDNA and catch is the common spatial pattern between the two data, which cannot explain by each terms of the equations. That is, $\theta$ can be interpreted as the spatial distribution of species we want to know.

@@

\newpage
\begin{figure}[h]
  \centering
  \includegraphics[width = 18cm]{idea.png}
  \caption{Conceptual diagram of this study.}
\end{figure}

>>>>

\newpage
\begin{linenumbers}
\setstretch{2}
\section{Introduction}
Understanding of spatial distribution of species and underling its mechanism is a major goal in ecology. 
Field surveys using environmental DNA (eDNA) are widely used for detecting invasive or rare species and hotspot of biodiversity %(面倒なのでレビュー論文を引用) 
because the surveys of eDNA are easy to detect occurrence of target species, non-invasiveness, and high cost effectiveness rather than previous direct sampling method (Rees et al. 2014; Thomsen \& Willerslev 2015) %Dorazioに引用されていたやつ．あとで再確認
However, uncertainty of the occurrence of eDNA is a issue in eDNA studies because various factors, such as biological and environmental features, intricately affect the shedding (i.e., production of eDNA from organisms) and degradation (i.e., decay of eDNA from a system) of eDNA (Fig. 1). Therefore, it is necessary to consider the spatial uncertainty included in eDNA to estimate the spatial distribution of species.

%However, a issue of eDNA is uncertainty of the occurrence of eDNA caused by various factors such as biology and environment (Fig. 1). 
%However, the occurrence of eDNA includes many types of uncertainties due to relating to environmental factors such as temperature and advection ().For example, in aquatic habitats, it is not sure whether target species are in a location or not when eDNA of target species is detected because eDNA are transported passively.Therefore, the consideration to the influence of environmental factors on eDNA is necessary for estimation of species distribution when we use eDNA methods.

@@

\flushleft{\textbf{2.2.3 Estimation of spatial distribution}}\\
To estimate the spatial distribution of four focal species using eDNA and catch data by considering with spatial  uncertainties of eDNA, we fitted the model (equation 1) to the presence/absence of eDNA and of catch collected in Tokyo Bay as follows:
%In this study, to estimate the spatial distribution of species from eDNA considering with spatial uncertainties, we make a integrated species distribution model using correlation method.
\[
\mathrm{logit} \ \ p_{e}(s_{i}) = \alpha_{e} + \sum_{k}f_{k}(x_{k}(s_{i})) + w \theta(s_{i}) + u_{e}(s_{i})
\]
\[
\mathrm{logit} \ \ p_{c}(s_{i}) = \alpha_{c} + \beta_{i} + \theta(s_{i}) + u_{c}(s_{i})
\]
where $\alpha$ is the intercept, and $x_{k}(s_{i})$ is the covariates at sites $i$ for occurrence probabilities of eDNA at sites $i$. In the study, seawater temperature, salinity, pH, and DO were used as covariates which effect on the occurrence of eDNA (i.e., $k = 4$). $u(s_{i})$ is spatial error that is specific for each data following multivariate normal distributions $\mathrm{MVN}(0, \mathbf{R})$, where the variance--covariance matrix $\mathbf{R}$ is a Mat\'{e}rn correlation function. $\theta$ which is shared between eDNA and catch is the common spatial pattern between the two data, which cannot explain by each terms of the equations. That is, $\theta$ can be interpreted as the spatial distribution of species we want to know. \textcolor{red}{共変量の非線形性について書く}Parameters in this model was estimated by Integrated Nested Laplace Approximation using using the R-INLA package (Lindgren, 2012) in \textcolor{red}{R 3.6.1 (R Development Core Team, 2019).}
\ \ \ \ \ \ \ \ \ \

@@

\newpage
\begin{figure}[h]
  \centering
  \includegraphics[width = 18cm]{fig1.png}
  \caption{Conceptual diagram of this study.}
\end{figure}
